Model to study co-evolution of trade an culture

### 2015-04-02 article.tex
todo

\begin{table}
\begin{center}
\begin{tabular}{@{}ll@{}}
\toprule
Parameter & Value \\
\midrule
Mutation probability & \\
Innovation probability & \\
CulturalStep &  10 \\
TradeThreshold & $\frac{Number of agent}{2}$ \\
TimeSteps & \\
\bottomrule
\end{tabular}
\caption{Table of parameters}\label{tab:parameters}
\end{center}
\end{table}

@@

In order to study a trading model two new innovation and imitation mechanisms have been introduced as explained in section~\ref{sec:}. These mechanisms are summarized in the table~\ref{tab:exp}. Each couple of innovation/imitation mechanism form one setup that is labelled with one later. Note that the ``neutral model" studied in the previous section corresponds to the setup A. All the runs presented in this section are done for 100000 steps with a innovation rate $\mu=.004$ and $\beta=.001$.

@@

\begin{table}[H]
	\centering
	\begin{tabular}{l c c}
		& Random Transmission & Eco Transmission \\
		$\mu$ & \specialcell{\raisebox{-.5\height}{\includegraphics[width=5cm]{img/ScoreEvolutionForA-G2N250.pdf}}\\Setup A}&\specialcell{\raisebox{-.5\height}{\includegraphics[width=5cm]{img/ScoreEvolutionForB-G2N250.pdf}} \\ Setup B} \\
		$\mu + \alpha$& \specialcell{\raisebox{-.5\height}{\includegraphics[width=5cm]{img/ScoreEvolutionForC-G2N250.pdf}} \\ Setup C}&\specialcell{\raisebox{-.5\height}{\includegraphics[width=5cm]{img/ScoreEvolutionForD-G2N250.pdf}} \\ Setup D}

@@

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=7cm]{img/ratioEvol.png}
	\end{center}
	\caption{Evolution of the difference $\dfrac{p(g_w)}{p(g_p)}-n(g_p)$ where $p(x_i)$ is the price for a good $i$, $n(x_i)$ its need, $g$ the produced good and $w$ the wanted}
	\label{fig:ratioEvol}
\end{figure}

>>>>

\begin{table}
\begin{center}
\begin{tabular}{@{}ll@{}}
\toprule
Parameter & Value \\
\midrule
Mutation probability & .004 \\
Innovation probability & .001\\
CulturalStep &  10 \\
TradeThreshold & 100  \\
TimeSteps & 200000 \\
\bottomrule
\end{tabular}
\caption{Table of parameters}\label{tab:parameters}
\end{center}
\end{table}

@@

In order to study a trading model two new innovation and imitation mechanisms have been introduced as explained in section~\ref{sec:}. These mechanisms are summarized in the table~\ref{tab:exp}. Each couple of innovation/imitation mechanism form one setup that is labelled with one letter. Note that the ``neutral model" studied in the previous section corresponds to the setup A. All the runs presented in this section are done for 200000 steps with a innovation rate $\mu=.004$ and $\beta=.001$.

@@

\begin{table}[H]
	\centering
	\begin{tabular}{l c c}
		& Random Transmission & Eco Transmission \\
		$\mu$ & \specialcell{\raisebox{-.5\height}{\includegraphics[width=5cm]{img/ScoreEvolutionForA-G2N250.pdf}}\\Setup A}&\specialcell{\raisebox{-.5\height}{\includegraphics[width=5cm]{img/ScoreEvolutionForB-G2N250.pdf}} \\ Setup B} \\
		$\mu + \alpha$& \specialcell{\raisebox{-.5\height}{\includegraphics[width=5cm]{img/ScoreEvolutionForC-G2N250.pdf}} \\ Setup C}&\specialcell{\raisebox{-.5\height}{\includegraphics[width=5cm]{img/ScoreEvolutionForD-G3N500.pdf}} \\ Setup D}

@@

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=7cm]{img/ClearingPriceDistanceEvolutionForD-G3N500.pdf}
	\end{center}
	\caption{Evolution of the difference $\dfrac{p(g_w)}{p(g_p)}-n(g_p)$ where $p(x_i)$ is the price for a good $i$, $n(x_i)$ its need, $g$ the produced good and $w$ the wanted}
	\label{fig:ratioEvol}
\end{figure}
